The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-10-26 paper/ms.tex
amalie figure

>>>>

\textcolor{red}{Paragraph on stellar modelling by Amalie}

\begin{figure*}
\noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}

\caption{\label{masses}
Using asteroseismic constraints (left) and asteroseismic and spectroscopic constraints jointly (right) we infer the masses of each star in the asteroseismic sample of giants.}
\end{figure*}
